Dynamic Stochastic Approximation Monte Carlo

### 2018-07-16 papers/histogram/sad.tex
start adding slow/fast output and adjusting scripts to plot it

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error.pdf}
  \caption{The average entropy error for each method is shown for $\lambda = 0.30$ with
  SAMC followed by TMMC serving as the `golden'
  standard.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error.pdf}
  \caption{The average entropy error is shown for $\lambda = 0.30$ with TMI acting as the
  `golden' standard.}\label{fig:n500-ff0.3}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.  This is exciting because we
    have different MC moves (slow, etc).}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-default.pdf}
  \caption{The average entropy error for each method is shown for $\lambda = 0.30$ with
  SAMC followed by TMMC serving as the `golden'
  standard.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-slow.pdf}
  \caption{The average entropy error for each method is shown for $\lambda = 0.30$ with
  SAMC followed by TMMC serving as the `golden'
  standard.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-fast.pdf}
  \caption{The average entropy error for each method is shown for $\lambda = 0.30$ with
  SAMC followed by TMMC serving as the `golden'
  standard.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error-default.pdf}
  \caption{The average entropy error is shown for $\lambda = 0.30$ with TMI acting as the
  `golden' standard.}\label{fig:n500-ff0.3}
\end{figure}
